---
title: "STAT 231: Problem Set 7B"
author: "Molly Cooper"
date: "due by 5 PM on Friday, October 30"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

This homework assignment is designed to help you futher ingest, practice, and expand upon the material covered in class over the past week(s).  You are encouraged to work with other students, but all code and text must be written by you, and you must indicate below who you discussed the assignment with (if anyone).  

Steps to proceed:

\begin{enumerate}
\item In RStudio, go to File > Open Project, navigate to the folder with the course-content repo, select the course-content project (course-content.Rproj), and click "Open" 
\item Pull the course-content repo (e.g. using the blue-ish down arrow in the Git tab in upper right window)
\item Copy ps7B.Rmd from the course repo to your repo (see page 6 of the GitHub Classroom Guide for Stat231 if needed)
\item Close the course-content repo project in RStudio
\item Open YOUR repo project in RStudio
\item In the ps7B.Rmd file in YOUR repo, replace "YOUR NAME HERE" with your name
\item Add in your responses, committing and pushing to YOUR repo in appropriate places along the way
\item Run "Knit PDF" 
\item Upload the pdf to Gradescope.  Don't forget to select which of your pages are associated with each problem.  \textit{You will not get credit for work on unassigned pages (e.g., if you only selected the first page but your solution spans two pages, you would lose points for any part on the second page that the grader can't see).} 
\end{enumerate}

```{r, setup, include=FALSE}
library(tidyverse)
library(ggnetwork)
library(igraph)

knitr::opts_chunk$set(
  tidy=FALSE,     # display code as typed
  size="small")   # slightly smaller font for code
```


\newpage 
# If you discussed this assignment with any of your peers, please list who here:

> ANSWER:

\newpage
# 1. More Migration

1a. Consider migration between the following countries: Brazil, Ghana, Great Britain, Honduras, India, South Korea, United States, and Vietnam.  Compare the TOTAL (males + females) migration between these countries over time.  In separate (directed) graphs for 1980 and 2000, visualize the network for the these countries with edge width and/or edge color corresponding to migration flow size.  Interpret the two graphs -- what *information in context* do they convey?

> ANSWER: Both graphs represent the migration patterns between Brazil, Ghana, Great Britain, Honduras, India, South Korea, United States, and Vietnam in 1980 and 2000, the width of the lines between countries represents the number of people migrating between each country in these years. The "1980 Migration" tells us that people most commonly moved between The United States and Great Britain, whereas people least often moved between Indonesian, Honduras, Brazil, and Ghana as well as Korea and India. Transitioning to the "2000 Migration", we see that the most popular movement is still between the US and Great Britain, whereas the least popular are now Vietnam to Brazil (or Brazil to Vietnam), Korea to Vietnam, Korea to Ghana, and Brazil to Vietnam. 

```{r, message = FALSE}
path_in <- '/Users/mollycooper/Git Hub/STAT-231-Molly/Homework'
MigrationFlows <- read_csv(paste0(path_in,"/MigrationFlows.csv"))

countries <- c("BRA","GBR","GHA","HND","IND","KOR", "USA", "VNM")

#Compare TOTAL Migration Over Time

#Creating Data Sets
DataOne <- MigrationFlows %>%
  select(origincode, destcode, Y1980) %>%
  filter(Y1980 > 0, origincode %in% countries, destcode %in% countries)
DataTwo <- MigrationFlows %>%
  select(origincode, destcode, Y2000) %>%
  filter(Y2000 > 0, origincode %in% countries, destcode %in% countries)

#Creating Migration Flows
Migration1980 <- graph_from_data_frame(DataOne, directed = TRUE)
Migration2000 <- graph_from_data_frame(DataTwo, directed = TRUE)

ggplot(data = ggnetwork(Migration1980)
       , aes(x = x, y = y, xend = xend, yend = yend)) +
  geom_edges(arrow=arrow(type="closed", length=unit(6,"pt"))
            , color = "gray50"
            , aes(size = Y1980)) +
  geom_nodes() +
  geom_nodelabel(aes(label =name)) +
  theme_blank() +
  ggtitle("1980 Migration") + 
  labs(size = "1980 Migration Flow")

ggplot(data = ggnetwork(Migration2000)
       , aes(x = x, y = y, xend = xend, yend = yend)) +
  geom_edges(arrow=arrow(type="closed", length=unit(6,"pt"))
            , color = "gray50"
            , aes(size = Y2000)) +
  geom_nodes() +
  geom_nodelabel(aes(label =name)) +
  theme_blank() +
  ggtitle("2000 Migration") + 
  labs(size = "2000 Migration Flow")
```

1b. Compute the *unweighted* in-degree for Brazil in this network from 2000, and the *weighted* in-degree for Brazil in this network from 2000.  In 1-2 sentences, interpret these numbers in context (i.e., without using the terms "in-degree" or "weighted").


> ANSWER:  There are 14 routes which map to Brazil as a destination from the countries listed and there were 20885 times people took routes that migrated into Brazil in 2000 from one of the countries listed. 

```{r}
#Calculating Unweighted In-Degree
strength(Migration2000, mode = "in")

#Calculating Weighted In-Degree
strength(Migration2000, weights = E(Migration2000)$Y2000, mode = "in")

```


1c. Among these same countries, idenitify the top 5 countries *of origin* and *of destination* (separately) in 1980 using (weighted) degree centrality.  Interpret this information.

> ANSWER: The top 5 countries of origin are: Great Britain, Korea, India, United States, and Vietnam, indicating that these five countries are the most centeral places of origin in this network. The top 5 countries of destination are: United States, Great Britain, India, Brazil, and Korea, this indicates that these five countries were the most central destinations in this pattern of migration. 

```{r}
#Calculating Countries of Origin
strength(Migration1980, weights = E(Migration1980)$Y1980, mode = "out")

#Calculating Countries of Destination
strength(Migration1980, weights = E(Migration1980)$Y1980, mode = "in")
```


1d. Among these same countries, idenitify the top 5 countries *of origin* and *of destination* (separately) in 2000 using (weighted) degree centrality.  Interpret this information.

> ANSWER: Top 5 Countries of Origin --> Great Britain, USA, India, Brazil, Vietnam
This information tells us that in 2000, within this migration flow, these 5 countries were most commonly migrated from (places of origin).
Top 5 Countries of Destination --> USA, Great Britain, India, Brazil Ghana
This information tells us that these 5 countries were most commonly migrated to in this network, ie. they were the most popular destinations. 
It's interesting to consider the differences in centrality between 1980 and 2000 in the context of wars, political climate, and economic development... these numbers clearly corrolate!


```{r}
#Calculating Countries of Origin
strength(Migration2000, weights = E(Migration2000)$Y2000, mode = "out")

#Calculating Countries of Destination
strength(Migration2000, weights = E(Migration2000)$Y2000, mode = "in")

```


1e. What is the diameter of this network in 2000? In 1-2 sentences, interpret this value.

> ANSWER: The diameter of the 2000 migration network is 2, which indicates that the farthest two countries nodes are from eachother is only 2 jumps away. 

```{r}
diameter(Migration2000, directed = TRUE)
```


1f. What is the density of this network in 2000? In 1-2 sentences, interpret this value.

> ANSWER:  *I made the assumption that you meant in 1980? 
In 1980, the migration flow has the exact same diameter with each country have nodes at most two hops away from one another. 

```{r}
diameter(Migration1980, directed = TRUE)
```


\newpage
# 2. Love Actually (OPTIONAL PRACTICE)

This problem is *optional* and will not be graded, but is given to provide additional practice interpreting networks and as another real-world example of network analysis that might be intriguing to film buffs. 

Consider the figure "The Two Londons of 'Love Actually'" in [this FiveThirtyEight article](https://fivethirtyeight.com/features/the-definitive-analysis-of-love-actually-the-greatest-christmas-movie-of-our-time/). 

2a. Based on this figure, is the network connected?  In 1-2 sentences, please explain.

> ANSWER: 

2b. Based on the figure, what is the (unweighted) degree for Emma Thompson?  What is the (unweighted) degree for Keira Knightley?  Explain what these values mean for these characters.

> ANSWER: 

2c. Based on the figure, for whom would the (unweighted) betweenness centrality measure be higher: Colin Firth or Hugh Grant?  Explain what this implies. 

> ANSWER:  